\vspace*{-0.2cm}

\section{Conclusions}
\label{sec:conclusions}

Time series anomaly detection is a challenging problem and an important area of research with many applications. % in many scientific, societal, and industrial domains. 
Despite the multitude of solutions proposed in the literature, we observe that there exists no method that outperforms all others when measured on large heterogeneous benchmarks. Based on our experimental evaluation %, we answer the questions of Section~\ref{sec:objective} as follows:
(cf. questions of Section~\ref{sec:objective}): 

\begin{enumerate}[noitemsep, topsep=0pt, parsep=0pt, partopsep=0pt, leftmargin=0.5cm]
	\item \textbf{Classification as Model selection}: We observe that time series classification methods accurately select anomaly detection models. Overall, Transformer and Convolutional-based model selection methods outperform each individual detector. Nevertheless, there is a large gap between the best method and the $Oracle$, motivating future work toward that direction.
	\item \textbf{Ensembling or selecting}: We observe that model selection is significantly more accurate than the Ensembling method.
	\item \textbf{Features or Raw values}: We observe that raw-based methods are more accurate on average than feature-based approaches.
	\item \textbf{Out-Of-Distribution}: (1) and (3) hold. However, for (2), \syl{we} observe that ensembling is more accurate than model selection when applied to time series very different from those in the training benchmark.
\end{enumerate}

The above observations point to promising directions for future work in AutoML frameworks that rely on model selection. %As mentioned in Section~\ref{exp:detectionvsclass}, 
Improving the rank prediction could significantly improve the anomaly detection accuracy. Moreover, model selection could be trained to choose the best compromise between accuracy and execution time, improving the overall inference time of model selection. %Finally, when applied to unsupervised settings, the accuracy gap between the best model selection and the $Oracle$ and the model selection methods' accuracy drop motivate future works in these directions.

\begin{acks}
Work partly supported by Meta Research and GENCI-IDRIS (Grants 2020-101471, 2021-101925, 2022-AD011012641R1).
\end{acks}

% \vspace{-0.1cm}
% \begin{acks}
% \vspace{-0.1cm}
% Work supported by HPC resources from GENCI-IDRIS (Grants 2020-101471, 2021-101925, 2022-AD011012641R1), and NVIDIA Corporation for the Titan Xp GPU donation used in this research.
% \end{acks}